SI

### 2021-02-17 ms/si.Rmd
update SI

```{r si-load-functions, cache = FALSE}
# Define functions specific to this file
plot_chamber_rh <- function (data, time_limits) {
  ggplot(data, aes(x = date_time, y = 0.01*rh)) +
    geom_line() +
    scale_x_datetime(limits = time_limits) +
    scale_y_continuous(label = label_percent(accuracy = 1)) +
    labs(y = "Relative humidity") +
    theme(
      legend.position = "none",
      axis.title.x = element_blank(),
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank())
}

plot_chamber_temp <- function (data, time_limits) {
  ggplot(data, aes(x = date_time, y = temp)) +
    geom_line() +
    scale_x_datetime(limits = time_limits) +
    scale_y_continuous(label = label_number(suffix = "\u00b0C", accuracy = 1)) +
    labs(y = "Temperature") +
    theme(
      legend.position = "none",
      axis.title.x = element_blank(),
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank())
}

plot_sporo_chamber_time <- function (data, time_limits) {
    ggplot(data, aes(x = species, ymin = pre, ymax = post, y = post, group = species_duration, linetype = dry_time)) +
    geom_linerange(position = position_dodge(0.5)) +
    geom_point(position = position_dodge(0.5)) +
    scale_y_datetime(limits = time_limits) +
    scale_x_discrete(labels = str_abbrev_sp_pretty) +
    scale_linetype_manual(values = c("15" = "solid", "2" = "solid")) +
    coord_flip() +
    labs(x = "Species") +
    theme(
      axis.title.x = element_blank(),
      axis.text.y = element_markdown(),
      legend.position = "none"
    )
}

plot_sporo_chamber <- function (sporo_times_data, filmy_dt_chamber_data, salt_select, k_select) {

  # Get mean times of each cluster of DT test samples for the selected drying salt
  sporo_clusters <- cluster_sporo_times(sporo_times_data, salt_select, k_select)

  # Calculate time range for the clustered data
  sporo_time_range <- c(min = min(sporo_clusters$pre), max = max(sporo_clusters$post))

  # Subset DT chamber data
  sporo_chamber_data <-
    filmy_dt_chamber_data %>% 
    filter(date_time >= sporo_time_range[["min"]], date_time <= sporo_time_range[["max"]], salt == salt_select)

  # RH plot
  rh_plot <- plot_chamber_rh(sporo_chamber_data, sporo_time_range)

  # Temp plot
  temp_plot <- plot_chamber_temp(sporo_chamber_data, sporo_time_range)

  # Dry times plot
  time_plot <- plot_sporo_chamber_time(sporo_clusters, sporo_time_range)

  # Combine plots
  rh_plot + temp_plot + time_plot + plot_layout(ncol = 1)
}

@@

# Subset DT chamber data
licl_chamber_data_2013 <-
  filter(filmy_dt_chamber, 
    date_time >= licl_time_range_2013[["min"]], 
    date_time <= licl_time_range_2013[["max"]], 
    salt == "LiCl")
licl_chamber_data_2014 <- 
  filter(filmy_dt_chamber, 
    date_time >= licl_time_range_2014[["min"]], 
    date_time <= licl_time_range_2014[["max"]], 
    salt == "LiCl") %>%
  # There are two sets of times: 2014-06-17 to 2014-07-02, and 2014-07-06 to 2014-07-08
  # Add a group for these so ggplot doesn't connect lines betweeen them
  mutate(
    day = yday(date_time),
    group = ifelse(day < 185, "a", "b"))

licl_chamber_data <- bind_rows(licl_chamber_data_2013, licl_chamber_data_2014)
licl_temp_range <- c(min(licl_chamber_data$temp), max(licl_chamber_data$temp))
licl_rh_range <- c(min(licl_chamber_data$rh), max(licl_chamber_data$rh))*0.01

# RH plot
licl_rh_plot_2013 <- plot_chamber_rh(licl_chamber_data_2013, licl_time_range_2013) +
  scale_y_continuous(limits = licl_rh_range, label = label_percent(accuracy = 1))

licl_rh_plot_2014 <- ggplot(licl_chamber_data_2014, aes(x = date_time, y = 0.01*rh, group = group)) +
  geom_line() +
  scale_x_datetime(limits = licl_time_range_2014) +
  blank_x_theme() +
  blank_y_theme() +
  theme(legend.position = "none")

# Temp plot
licl_temp_plot_2013 <- plot_chamber_temp(licl_chamber_data_2013, licl_time_range_2013) +
  scale_y_continuous(limits = licl_temp_range, label = label_number(suffix = "\u00b0C", accuracy = 1))

licl_temp_plot_2014 <- ggplot(licl_chamber_data_2014, aes(x = date_time, y = temp, group = group)) +
  geom_line() +
  scale_x_datetime(limits = licl_time_range_2014) +
  blank_x_theme() +
  blank_y_theme() +
  theme(legend.position = "none")

# Dry times plot
licl_time_plot_2013 <- plot_sporo_chamber_time(licl_clusters, licl_time_range_2013) +
  labs(y = "2013") +
  theme(axis.title.x = element_text()) 
licl_time_plot_2014 <- plot_sporo_chamber_time(licl_clusters, licl_time_range_2014)  +
  labs(y = "2014")  +
  theme(axis.title.x = element_text()) +
  blank_y_theme()

# Combine plots
licl_temp_plot_2013 + licl_temp_plot_2014 + 
  licl_rh_plot_2013 + licl_rh_plot_2014 + 
  licl_time_plot_2013 + licl_time_plot_2014 + 
  plot_layout(ncol = 2) +
  plot_annotation(title = "a")
```

@@

# Temp plots
nacl_temp_plot_2012 <- 
  ggplot(
    nacl_chamber_data_2012, 
    aes(x = date_time, y = temp)
  ) +
  geom_line(size = 0.25) +
  scale_x_datetime(limits = nacl_time_range_2012) +
  scale_y_continuous(
    label = label_number(suffix = "\u00b0C", accuracy = 1), 
    limits = nacl_temp_range) +
  labs(
    y = "Temperature",
    color = "Data logger\nserial no.",
    title = "2012") +
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()) +
  blank_y_theme() +
  guides(color = "none")

nacl_temp_plot_2013 <- 
  ggplot(
    nacl_chamber_data_2013, 
    aes(x = date_time, y = temp, color = serial_no)
  ) +
  geom_line(size = 0.25) +
  scale_color_manual(values = serial_no_cols) +
  scale_x_datetime(limits = nacl_time_range_2013) +
  scale_y_continuous(
    label = label_number(suffix = "\u00b0C", accuracy = 1), 
    limits = nacl_temp_range) +
  labs(
    y = "Temperature",
    color = "Data logger\nserial no.",
    title = "2013") +
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()) +
  blank_y_theme() +
  guides(color = "none")

nacl_temp_plot_2014 <- 
  ggplot(
    nacl_chamber_data_2014, 
    aes(x = date_time, y = temp, color = serial_no, group = interaction(group, serial_no))
  ) +
  scale_color_manual(values = serial_no_cols) +
  geom_line(size = 0.25) +
  scale_x_datetime(limits = nacl_time_range_2014) +
  scale_y_continuous(
    label = label_number(suffix = "\u00b0C", accuracy = 1), 
    limits = nacl_temp_range) +
  labs(
    y = "Temperature",
    color = "Data logger\nserial no.",
    title = "2014") +
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()) +
  guides(color = "none")

>>>>

```{r si-load-functions, cache = FALSE}
# Define functions specific to this file
plot_chamber_rh <- function (data, time_limits) {
  ggplot(data, aes(x = date_time, y = 0.01*rh)) +
    geom_line(size = 0.25) +
    scale_x_datetime(limits = time_limits) +
    scale_y_continuous(label = label_percent(accuracy = 1)) +
    labs(y = "Relative humidity") +
    theme(
      legend.position = "none",
      axis.title.x = element_blank())
}

plot_chamber_temp <- function (data, time_limits) {
  ggplot(data, aes(x = date_time, y = temp)) +
    geom_line(size = 0.25) +
    scale_x_datetime(limits = time_limits) +
    scale_y_continuous(label = label_number(suffix = "\u00b0C", accuracy = 1)) +
    labs(y = "Temperature") +
    theme(
      legend.position = "none",
      axis.title.x = element_blank())
}

plot_sporo_chamber_time <- function (data, time_limits) {
    ggplot(data, aes(x = species, ymin = pre, ymax = post, y = post, group = species_duration, linetype = dry_time)) +
    geom_linerange(position = position_dodge(0.5)) +
    geom_point(position = position_dodge(0.5)) +
    scale_y_datetime(limits = time_limits) +
    scale_x_discrete(labels = str_abbrev_sp_pretty) +
    scale_linetype_manual(values = c("15" = "solid", "2" = "solid")) +
    coord_flip() +
    labs(x = "Species") +
    theme(
      axis.title = element_blank(),
      axis.text.y = element_markdown(),
      legend.position = "none"
    )
}

@@

# Subset DT chamber data
licl_chamber_data_2012 <- 
  filter(filmy_dt_chamber, 
         date_time > "2012-07-31 18:10:00 UTC", 
         date_time < "2013-01-01 00:10:00 UTC",
         salt == "LiCl")

licl_time_range_2012 <- c(min = min(licl_chamber_data_2012$date_time), max = max(licl_chamber_data_2012$date_time))

licl_chamber_data_2013 <-
  filter(filmy_dt_chamber, 
    date_time >= licl_time_range_2013[["min"]], 
    date_time <= licl_time_range_2013[["max"]], 
    salt == "LiCl")
licl_chamber_data_2014 <- 
  filter(filmy_dt_chamber, 
    date_time >= licl_time_range_2014[["min"]], 
    date_time <= licl_time_range_2014[["max"]], 
    salt == "LiCl") %>%
  # There are two sets of times: 2014-06-17 to 2014-07-02, and 2014-07-06 to 2014-07-08
  # Add a group for these so ggplot doesn't connect lines betweeen them
  mutate(
    day = yday(date_time),
    group = ifelse(day < 185, "a", "b"))

licl_chamber_data <- bind_rows(licl_chamber_data_2012, licl_chamber_data_2013, licl_chamber_data_2014)
licl_temp_range <- c(min(licl_chamber_data$temp), max(licl_chamber_data$temp))
licl_rh_range <- c(min(licl_chamber_data$rh), max(licl_chamber_data$rh))*0.01

# Temp plots
licl_temp_plot_2014 <- ggplot(licl_chamber_data_2014, aes(x = date_time, y = temp, group = group)) +
  geom_line(size = 0.25) +
  scale_x_datetime(limits = licl_time_range_2014) +
  scale_y_continuous(
    label = label_number(suffix = "\u00b0C", accuracy = 1), 
    limits = licl_temp_range) +
  labs(
    y = "Temperature",
    title = "2014") +
  theme(
    plot.title = element_text(hjust = 0.5, size = 11),
    legend.position = "none") +
  blank_x_theme()

licl_temp_plot_2013 <- plot_chamber_temp(licl_chamber_data_2013, licl_time_range_2013) +
  scale_y_continuous(limits = licl_temp_range) +
  labs(title = "2013") +
  theme(plot.title = element_text(hjust = 0.5, size = 11)) +
  blank_y_theme() +
  blank_x_theme()

licl_temp_plot_2012 <- plot_chamber_temp(licl_chamber_data_2012, licl_time_range_2012) +
  scale_y_continuous(limits = licl_temp_range) +
  labs(title = "2012") +
  theme(plot.title = element_text(hjust = 0.5, size = 11)) +
  blank_y_theme() +
  blank_x_theme()

# RH plots
licl_rh_plot_2014 <- ggplot(licl_chamber_data_2014, aes(x = date_time, y = 0.01*rh, group = group)) +
  geom_line(size = 0.25) +
  scale_x_datetime(limits = licl_time_range_2014) +
  scale_y_continuous(
    label = label_percent(accuracy = 1), 
    limits = licl_rh_range) +
  labs(y = "Relative humidity") +
  theme(legend.position = "none") +
  blank_x_theme()

licl_rh_plot_2013 <- plot_chamber_rh(licl_chamber_data_2013, licl_time_range_2013) +
  scale_y_continuous(limits = licl_rh_range, label = label_percent(accuracy = 1)) +
  blank_y_theme() +
  blank_x_theme()

licl_rh_plot_2012 <- plot_chamber_rh(licl_chamber_data_2012, licl_time_range_2012) +
  scale_y_continuous(limits = licl_rh_range, label = label_percent(accuracy = 1)) +
  blank_y_theme()

# Dry times plot
licl_time_plot_2013 <- plot_sporo_chamber_time(licl_clusters, licl_time_range_2013) +
  blank_y_theme()
licl_time_plot_2014 <- plot_sporo_chamber_time(licl_clusters, licl_time_range_2014)

# Combine plots
licl_temp_plot_2014 + licl_temp_plot_2013 + licl_temp_plot_2012 +
  licl_rh_plot_2014 + licl_rh_plot_2013 + licl_rh_plot_2012 +
  licl_time_plot_2014 + licl_time_plot_2013 + plot_spacer() +
  plot_layout(ncol = 3, nrow = 3, guides = "collect") +
  plot_annotation(title = "a")
```

@@

# Temp plots
nacl_temp_plot_2012 <- 
  ggplot(
    nacl_chamber_data_2012, 
    aes(x = date_time, y = temp)
  ) +
  geom_line(size = 0.25) +
  scale_x_datetime(limits = nacl_time_range_2012) +
  scale_y_continuous(
    label = label_number(suffix = "\u00b0C", accuracy = 1), 
    limits = nacl_temp_range) +
  labs(
    y = "Temperature",
    color = "Data logger\nserial no.",
    title = "2012") +
  theme(
    plot.title = element_text(hjust = 0.5, size = 11),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()) +
  blank_y_theme() +
  guides(color = "none")

nacl_temp_plot_2013 <- 
  ggplot(
    nacl_chamber_data_2013, 
    aes(x = date_time, y = temp, color = serial_no)
  ) +
  geom_line(size = 0.25) +
  scale_color_manual(values = serial_no_cols) +
  scale_x_datetime(limits = nacl_time_range_2013) +
  scale_y_continuous(
    label = label_number(suffix = "\u00b0C", accuracy = 1), 
    limits = nacl_temp_range) +
  labs(
    y = "Temperature",
    color = "Data logger\nserial no.",
    title = "2013") +
  theme(
    plot.title = element_text(hjust = 0.5, size = 11),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()) +
  blank_y_theme() +
  guides(color = "none")

nacl_temp_plot_2014 <- 
  ggplot(
    nacl_chamber_data_2014, 
    aes(x = date_time, y = temp, color = serial_no, group = interaction(group, serial_no))
  ) +
  scale_color_manual(values = serial_no_cols) +
  geom_line(size = 0.25) +
  scale_x_datetime(limits = nacl_time_range_2014) +
  scale_y_continuous(
    label = label_number(suffix = "\u00b0C", accuracy = 1), 
    limits = nacl_temp_range) +
  labs(
    y = "Temperature",
    color = "Data logger\nserial no.",
    title = "2014") +
  theme(
    plot.title = element_text(hjust = 0.5, size = 11),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()) +
  guides(color = "none")
